
\documentclass[letterpaper,10pt]{article}
\usepackage[margin=3cm]{geometry}
\usepackage{parskip}
\usepackage{array}
\usepackage{hyperref}
\newcommand{\tab}{\hspace*{0.5in}}
\raggedright

\begin{document}
\pagestyle{empty}
\small

\section*
\textbf{\LARGE{Archana G}} \\
AE - 10/22, 10\textsuperscript{th} Main Road, \\
Anna Nagar, Chennai - 600 040. \\
\textbf{Ph no } : +91-9444059080 \\
\textbf{Email } : archana.gurusamy@gmail.com
\vspace{0.1in}
\hline

\subsection*{Career Objective}
To employ my knowledge in securing a professional career as a Software Developer with opportunities for challenges and career advancement, while gaining knowledge of new skills and expertise.

\subsection*{Education}
\begin{tabular*}{7in}{@{\extracolsep{\fill}}||p{1.2in}||p{1.5in}||p{1.2in}||p{0.8in}||p{1in}||}
\hline
\hline
\textbf{Course} & \textbf{Instituition} & \textbf{Board} & \textbf{Academic Year} & \textbf{\% Obtained} \\
\hline
\hline
Diploma in Java Technologies & NIIT Pvt.Ltd & Sun Educational Services & 2011 & 82\% \\
\hline
\hline
B.E(CSE) & KCG College of Technology & Anna University & 2007-2011 & 81.65\% \\
\hline
\hline
12\textsuperscript{th} Std & Grace Matriculation HSS & State Board & 2006-2007 & 88.83\% \\
\hline
\hline
10\textsuperscript{th} Std & Anna Adarsh Matriculation HSS & Matric & 2003-2004 & 94.82\% \\
\hline
\hline
\end{tabular*}

\subsection*{Technical Skills}
\begin{itemize}
\item Developing Java Technology applications with \textbf{Swing GUI, Console I/O streams and Multithreaded programming}.
\item Good understanding of \textbf{OOAD using UML}.
\item Applying \textbf{frameworks and patterns} to design a software system.
\item Designing \textbf{user friendly interfaces} for an appclient/web/enterprise application.
\item Building \textbf{web applications} from \textbf{JSP and servlet} technologies.
\item Creating robust web applications with \textbf{Struts, session management, filters and database integration}.
\item Creating easy to maintain JSP pages using \textbf{EL, JSTL, and Struts Tiles} framework.
\item Developing business components with \textbf{Enterprise Java Beans} Technology.
\item Developing Java EE Technology applications using \textbf{EJB session beans, Message-Driven Beans, interceptors and entity classes}.
\item Implementing CMT and BMT transactions using JTA.
\item Working with JPA and using JPQL to query entities in relational databases.
\item Using JAAS and PAM to implement Java EE Security.
\item Developing Java EE Technology applications with \textbf{messaging, transactions, timer functionality and web security}.
\end{itemize}

\subsection*{Software Proficiency}
\begin{itemize}
\item \textbf{Core Java Technologies} : Java SE \linebreak
\item \textbf{Web Application Development} : Servlets, JSP, Struts, Java Beans, HTML, JavaScript, CSS \linebreak
\item \textbf{Enterprise Application Development} : EJB 3.0 and other Java EE Technologies \linebreak
\item \textbf{Database technologies} : Oracle 9i/10g/11g, MS SQL Server, MySql, MS Access \linebreak
\item \textbf{IDEs} : Eclipse, NetBeans \linebreak
\item \textbf{Application tools} : Rational Rose, Microsoft Visio, git \linebreak
\item \textbf{\emph{Also knowledgeable in}} : C, Python, JUnit, Linux, XML, JSF 
\end{itemize}

\subsection*{Projects}
You can see some of my works at: \newline
\url{https://github.com/archugs}

\subsection*{International certifications}
Scored 91\% in Oracle Certified Professional, Java SE 6 Programmer

\subsection*{Academic Achievements}
\begin{itemize}
\item Secured centum in Mathematics-VI in B.E 6th semester.
\item Secured school first in 10th Matriculation Examination.
\item Secured school second in 12th State Board Examination.
\item Secured centum in Mathematics and Biology in Matriculation Examination.
\item Achieved '\emph{General Proficiency}' award in 9th and 10th standard.
\end{itemize}

\subsection*{Personal Traits}
\begin{itemize}
\item Comprehensive problem solving abilities
\item Self-motivated, ability to work with little/no supervision
\item Enthusiastic, knowledge-hungry learner, eager to meet new challenges and assimilate new concepts \item Passion towards work, dedicated and hard-working
\end{itemize}


\subsection*{Co-Curricular Activities}
\begin{itemize}
\item Participant hacker of Yahoo Open Hack India 2011 to be held in July 30, 2011.
\item Secured National Rank of 945 out of 37693(\textbf{Top 2\%}) in 7th \textbf{National IT Aptitude Test} by NIIT in March, 2011 
\item Attended a \textbf{technical workshop} on '\emph{Object Oriented Programming using Java}' conducted by NIIT, Pvt.Ltd
\item	Attended a \textbf{tech-talk} on '\emph{Android}' conducted at NIIT, Pvt.Ltd
\item Participated in \textbf{website development} for college symposium.
\item Participated in \textbf{inter-school story-writing} competition.
\end{itemize}

\subsection*{Interests}
\begin{itemize}
\item Writing short stories 
\item Reading detective and fantasy story books, regular reader of 'Reader's Digest' magazine
\item Traveling to new places, trekking and other adventures
\item Socializing with geeks and other like-minded people
\end{itemize}

\subsection*{Public Profile}
\begin{itemize}
\item \textbf{Blog: }\url{http://archugs.blogspot.com/}
\item \textbf{Twitter: } \url{http://twitter.com/#!/archugs}
\end{itemize}

\subsection*{Personal Profile}
\begin{tabular}{l@{\tab:\tab}l}
\textbf{Name}&Archana.G \\
\textbf{Father's Name}&Gurusamy.S \\
\textbf{Date of Birth}&21-Mar-1989 \\
\textbf{Permanent Address}&AE-10/22, 2\textsuperscript{nd} street,\\
 &10\textsuperscript{th} Main Road, \\
 &Anna Nagar, Chennai - 600 040. \\
\textbf{Email id}&archana.gurusamy@gmail.com \\
\end{tabular*}

\subsection*{References}
\begin{enumerate}
\item \textbf{Professor T.Ravi}
\newline
Head of CSE Department
\newline
KCG College of Technology,
\newline
Chennai.
\item \textbf{Professor S.Cloudin}
\newline
Assistant Head of Department
\newline
KCG College of Technology,
\newline
Chennai.
\end{enumerate}

\subsection*{Declaration}
\emph{\textbf{I, hereby declare that the details furnished above are true to the extent of my knowledge.}}
\newline
\flushright \textbf{Archana.G}
\end{document}